---
title: "miniTidyR"
author: "Huijue Chen, Orphelia Ellogne, Luo Yang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{miniTidyR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In this package we re-implemented R’s `gather`, `spread`, and `drop_na` functions that exist in `tidyverse`.

## Functions

`my_gather(data, keyname="key",valuename="value",chosen_cols)`

Transform a data from wide to long by combining columns. For selected columns, put the columns names into a column of keys, and the values into a column of values.

- data: A data frame
- keyname: Name of new key column, a string
- valuename: Name of new value column , a string
- chosen_cols: Name of columns to be gathered, a list

`my_spread(data, keycol, valcol)` 

Transform a data from long to wide.  Select a ‘key’ column whose content will be the names of the new columns. Select a ‘value’ column whose content will be the values of the new columns.

- keycol: Name of column whose content will be the names of the new columns, a string
- valcol: Name of column whose content will be the values of the new columns, a sting
- data: A data frame

`my_dropna(input_dataframe)`

Remove rows that contain `NA` values from a data frame.

- input_dataframe: A data frame

## Examples

```{r}
# load the package
library(miniTidyR)
```

```{r}
# example for my_dropna
df1 <- data.frame(A = c(12,25,NA,45), B = c(12,NA,30,45))
my_dropna(df1)
```

```{r}
# example for my_gather
df2 <- data.frame(Groups = c("A","B"), Married = c(12,25), Other = c(100,55))
my_gather(df2, "Status", "Count", list("Married","Other"))
```

```{r}
# example for my_spread
df3 <- data.frame(Name = c("A","A","B","B"), key = c("Age","Weight","Age","Weight"), value = c(45,80,30,70))
my_spread(df3,'key','value')
```